Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-06-02 manuscript.Rmd
update code for reverse coding

# rename variables for a final time
ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
rapport <- paste0("rapport", 1:16)
personality <- map(c("perceiver_trait", "target_trait", "judgment_trait"),
                   ~ paste0(.x, 1:26)) %>% unlist()
affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
              ~ paste0(.x, 1:120)) %>% unlist()
sbw <- paste0("swb", 1:5)
informant <- paste0("informant_trait", 1:26)

@@

df_reverse <- 
  df %>% 
  select(perceiver_id:group_id,
         negative_keyed_items)

df_reverse <- 
df_reverse %>% 
  mutate(across(all_of(negative_keyed_items), subtract_8)) %>% 
  rename_at(vars(negative_keyed_items), ~ paste0(negative_keyed_items, "rc"))

df <- left_join(df, df_reverse)
```

@@

Table 1 represents descriptive statistics for all the variables in the present study.

@@

```{r}
# personality
samdata <- import(here::here("data", "samdata.csv"))

samdata <-
  samdata %>% 
  mutate(

@@

## null model
null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
               data = samdata)

@@

samEAC_null <- lmer (Part ~ 1 + 
                  (1|PerUn) + 
                  (1|TarUn) + 
                  (1|DyUn), 
                data = samEACaggdata)

sjPlot::tab_model(samEAC_null)
```

>>>>

# rename variables for a final time
ids <- paste(c("perceiver", "target", "dyad", "group"), "id", sep = "_")
rapport <- paste0("rapport", 1:16)
personality <- map(c("perceiver_trait", "judgment_trait", "target_trait"),
                   ~ paste0(.x, 1:26)) %>% unlist()
affect <- map(c("perceiver_affect", "target_affect", "judgment_affect"),
              ~ paste0(.x, 1:120)) %>% unlist()
sbw <- paste0("swb", 1:5)
informant <- paste0("informant_trait", 1:26)

@@

df <- 
  df %>% 
  mutate_at(list(rc = ~subtract_8(.)),
            .vars = vars(negative_keyed_items)
            )

@@

Table 1 represents descriptive statistics as well as internal consistency metrics (i.e., alpha and omega) for predictors of interpersonal accuracy.

@@

```{r, include = FALSE}
# Create, clean and format data for analyses
## Personality

```{r}
# personality
df_personality <- import(here::here("data", "samdata.csv"))

df_personality <-
  df_personality %>% 
  mutate(

@@

## null model
null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), 
               data = df_personality)

@@

samEAC_null <- lmer (Part ~ 1 + 
                  (1|PerUn) + 
                  (1|TarUn) + 
                  (1|DyUn) +
                    (1|Group), 
                data = samEACaggdata)

sjPlot::tab_model(samEAC_null)

summary(samEAC_null)
```
